Matching ontologies with distributed word embeddings

### 2016-07-06 Paper/Draft.tex
All TODOs except intro and conclusion done

 \usepackage[utf8]{inputenc}
 \usepackage[titletoc]{appendix}
 \usepackage{listings}
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage{float}
 \usepackage{caption}
 \usepackage[export]{adjustbox}
 \usepackage{url}
 \usepackage{subcaption}
 \usepackage{multirow}

@@

 \pagenumbering{roman}
 \section*{Acknowledgements}
 \section*{Abstract}

@@

@@

 An example of an inter-knowledge base relation is shown in Figure \ref{merge_graph}. If these relations can be predicted, multiple knowledge bases can be aligned. Doing ontology alignment using these word embeddings is the goal of this work.
 \paragraph{}
 Currently, knowledge base and ontology alignment techniques do not make use of embeddings. Since embedding models have good performance on intra-knowledge base relation prediction, they should also work well on ontology alignment.

@@

 \subsection{Hypothesis} \label{hypotheses}

 \begin{center}
 \textit{Matchers that use a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
 \end{center}

 To prove this hypothesis, I must proof the following points:
 \begin{itemize}
 \item The algorithm uses distributed representations of concepts.
 \item The algorithm finds relationships between concepts in ontologies.
 \item The algorithm performs better.
 \end{itemize}

 \paragraph{}
 This hypothesis is true for distributed representations matching in general if it is true for one distributed representation matcher. Therefore to test the hypothesis, I must test it for every distinct implementation of the matcher.

 \subsection{Overview}
 This report is structured as follows: firstly, I will give all the required background information required to understand the context and the algorithms I will use. Then, I will describe the method, which includes the design of the algorithm and the evaluation method. The last two sections are the results and the joint conclusion and discussion, which interpret the results.

@@

 \subsubsection{Example} \label{example}
 In this section I will give an example of a pair of anatomical ontologies with their alignment. This example will be used throughout this work.

@@

 \begin{itemize}
  \item The problem I am trying to solve is the problem of differently labelled nodes referring to the same concept. For example \emph{writer} and \emph{author} will not be matched by a string matcher, but should be matched. The two concepts may also have different labels in their context even though their contexts refer to the same concepts.
  \item The size of the training corpus should be large enough for proper representation to be learned for every concept. It should also be relevant to the labels that are in the ontologies. This is a problem since the ontologies may be relatively small, so they need to be extended while keeping relevance.
  \item Some labels may be ambiguous, for example homonyms, which are concepts that have the same label but represent a different context.
 \end{itemize}

@@

 \subsubsection{Mice and men}
 The first data set considered consists of two anatomical ontologies. The first ontology describes the anatomy of mice and the second ontology the anatomy of men. Since they are similar creatures, there are many correspondences between the anatomy. The ontologies contain X and Y nodes, and X and Y edges, respectively. There are Z correspondences between the two ontologies.
 \paragraph{}
 The ontology is structured as a hierarchical tree with the only label being \emph{subClassOf}. This poses a few problems for some of the implementations as they take into account the edge labels. Since there are no edge labels, these implementations will not be different from their edge-less counterparts.
 \subsubsection{Medical}
 The second data set is larger, boasting X and Y medical concepts with X and Y relations. There are Z correspondences between the two ontologies. This data set has N different edge labels.

@@

 %TODO per algorithme uitleggen: hoe het werkt. Waarom gekozen. Plaatjes. Volgorde van kiezen (ik denk dat deze beter past) en bij resultaten bespreken of deze volgorde klopt.

@@

@@

  %TODO implement

@@

  It is possible to increase the number of examples that the algorithm considers by using DeepWalk. DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal word embedding model. This has the advantage of having a wider neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm. It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours. %TODO ref sentences

@@

  Possible reasons for the data causing bad results include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm. For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels. %TODO sowieso aanpassen maar ook aanpassen als ik 3e dataset heb.
  \paragraph{}
 The algorithm has been run on multiple data sets which are different. Despite that there is no significant difference in performance. For example, compare the F-measures for the medical dataset and the anatomy dataset. From Section \ref{results} we can see that both F-measures improve over the baselines, therefore the datasets used do not seem to influence the algorithm by too much.

 %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
 %Deepwalk paper ook kleine data
 %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
 %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
  \subsubsection{The system}
  Since the system parts are connected in sequence, if any of the steps in the software system contains an error, the whole system fails. This could cause all algorithms to learn badly or the results to be misinterpreted. The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers. If all of these systems work properly, the system is not the reason for the underperformance. I will analyse every part except for the context extractor, which will be analysed in the next section.

@@

  The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing ontology. The KD-tree has been tested by its creator and as such does not contain errors.
  \paragraph{Data loading}
  Since the preprocessing and context extraction works, we can conclude that the data is also loaded properly.
  \paragraph{Statistics and visualisation}
  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
  \paragraph{}
  Since every part works, the system is not faulty. %TODO kan beter

@@

  \subsubsection{Context extraction} \label{contextextraction}
  There are different context extractors for some of the different algorithms. I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model. If all three work well, the context extractors are not the cause of the underperformance.
  \paragraph{}
  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}. Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
  \paragraph{}
  For the Node2vec algorithms, the context extraction is more advanced. All edges are extracted from the ontology using Jena. Then, for every node the context is decided as every node it has an edge with. In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness. For the algorithms that also use the edge labels for context, double the context size is expected.
  \paragraph{}
  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up. For example "Adrenal vein" can be split up into "Adrenal" and "vein".
  The pre-trained model does not use any other form of context integration.
  \paragraph{}
  First, I obtained the number of edges from VOWLview\cite{vowlview}, an ontology graphing program, which looks like Figure \ref{vowlfig}. This was necessary since the creators of the data did not share how many edges were in the database. With the actual number of edges, obtained, it is possible to compare them with the number of edges found. If these match, the context extraction works.

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{plots/vowlview}
  \caption[]{}
  \label{vowlfig}
  \end{figure}

@@

 \subsubsection{Example: DeepWalk sentences} \label{sentences}

 %TODO

 \newpage
 \subsection{Evaluation}
 The goal of this study is to see if the developed ontology matching algorithm performs better than the best existing matchers. In this section I will define better.
 \subsubsection{Evaluation methods} \label{EvaluationMethods}
 Since for the used data the ground truth is available, comparison is straightforward. Namely, the algorithm that finds the most items that are also in the ground truth in the lowest number of attempts. This definition, however, has two parts: the number of correct attempts and the total number of attempts. This makes it hard to compare two algorithms, as one may be better with few attempts allowed whereas the other may be better with more attempts allowed.

@@

 %TODO F-pieken aanwijzen.
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec.}
   \label{ROC_untrained}
  \end{figure}

@@

 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Generic_ROC}
   \caption[Precision-recall curve pre-trained mice]{Pretrained Word2vec algorithm.}
   \label{ROC_generic}
   \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/trained_ROC}
   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
   \label{ROC_trained}
  \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Alternative_ROC}
   \caption[Precision-recall curve DeepWalk mice]{Alternative DeepWalk algorithm.}
   \label{ROC_alternative}
  \end{subfigure}
  \caption{Precision-recall trade-off curve for the results of three more algorithms.}
  \end{figure}
   \subsubsection{Medical data}
   TBD

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Label Match & 0.6926 & 0.4905 \\
  Random & 0.6926 & 0.4905 \\
  Generic & 0.6372 & 0.3874 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Deepwalk & 0.6926 & 0.4906 \\
  Alternative & 0.6372 & 0.4905 \\
  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD

 \newpage
 \subsection{Interpretation}
 \subsubsection{Unexpected results}
 \subsubsection{Expected results}

@@

 \subsection{Conclusions} \label{conclusions}
 The goal of this study was to answer the research question from Section \ref{researchquestion}:

@@

\paragraph{The algorithm uses distributed representations of concepts}
 From Section \ref{implementations} it is clear that every single algorithm uses distributed representations. To summarize:
\begin{description}
\item[pre-trained Word2vec] Uses existing distributed representations on every word in a label.
\item[Node2vec] All implementations of the Node2vec algorithms, monodirection, bidirectional and multi-sense, convert nodes into vectors.
\item[DeepWalk] Trains a normal distributed representation model on labels with the context generated from a random walk.
\end{description}
\paragraph{The algorithm finds relationships between concepts in ontologies}
This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
\paragraph{The algorithm performs better than the best matcher}

Not yet.

I compared the results of the algorithms with AML, the best existing matcher. All algorithms perform below AML. However, there is potential for better performance as we can see in Section \ref{discussion}.
\paragraph{}
 Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}.
 \paragraph{}
The results from all the different evaluation measures are in agreement. From those results we can conclude the following:

@@

 \subsection{Discussion} \label{discussion}
 %TODO gooi weg wat niet meer waar is

@@

 \section{Bibliography} %Fix

>>>>

 \usepackage[utf8]{inputenc}
 \usepackage[titletoc]{appendix}
 \usepackage{listings}
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage{float}
 \usepackage{caption}
 \usepackage[export]{adjustbox}
 \usepackage{url}
 \usepackage{subcaption}
 \usepackage{multirow}
 \usepackage[dvipsnames]{xcolor}
 \usepackage[nottoc,numbib]{tocbibind}

@@

 \pagenumbering{roman}
 \section*{Acknowledgements}
 Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor - Kennis enthusiasme en als het tegenzat kon hij me toch motiveren.
 Sanna Dinh, my partner - Nachtenlang opgebleven om het schrijfwerk en plaatjes
 Jeroen Vuurens, Delft University of Technology - Sparren over word2vec
 Xander Wilcke - Inspireren over het Semantisch Web
 Marianne - op de gekste tijdstippen skypen en proof-readen
 Suzan Verberne, professor at the Radboud University of Nijmegen - Nakijken
 Flynn, my pug - For the fresh air when I needed a minute to relax

 \section*{Abstract}
 McCallum proposed using distributed word embeddings for knowledge base completion, the problem of finding relations \textit{within} a knowledge base. In this study distributed word embeddings were used for ontology matching, the problem of finding relations \textit{between} knowledge bases. To test if distributed word embeddings also work on ontology matching, multiple algorithms that adapt these embeddings to ontology graphs were implemented.

 The conclusion is that distributed word embeddings can be applied to ontology matching. The performance is not as good as the state-of-the-art methods yet. However, distributed word embeddings have potential to improve with more data as opposed to current methods which are hand-crafted.

@@

 %TODO leg uit waarom intra implies inter
 %TODO maak duidelijk dat het \textit{mijn} idee was om inter te doen

@@

 An example of an inter-knowledge base relation is shown in Figure \ref{merge_graph}. If these relations can be predicted, multiple knowledge bases can be aligned. Doing ontology alignment using these word embeddings is the goal of this work.
 \paragraph{}
 Currently, knowledge base and ontology alignment techniques do not make use of embeddings. Since embedding models have good performance on knowledge base reconstruction\cite{universalschema}, they should also work well on ontology alignment.

@@

 To answer the research question, I must investigate the following points:
 \begin{itemize}
 \item The algorithm uses distributed representations of concepts.
 \item The algorithm finds relationships between concepts in ontologies.
 \item The algorithm performs well.
 \end{itemize}

 The answer is positive for distributed representations matching in general if it is positive for one distributed representation matcher.

 \subsection{Overview}
 This report is structured as follows: firstly, I will give all the required background information required to understand the context and the algorithms I will use. Then, I will describe the method, which includes the design of the algorithm and the evaluation method. The last two sections are the results and the joint conclusion and discussion, which interpret the results.
 %TODO dieper of weg

@@

 \subsubsection{Example} \label{example}
 In this section I will give an example of a pair of anatomical ontologies with their alignment, which will be used throughout this work.

@@

 \begin{itemize}
  \item The problem I am trying to solve is the problem of differently labelled nodes referring to the same concept. For example \emph{writer} and \emph{author} will not be matched by a string matcher, but should be matched. The two concepts may also have different labels in their context even though their contexts refer to the same concepts.
  \item The size of the training corpus should be large enough for proper representation to be learned for every concept. This is a problem since the ontologies may be relatively small. 
  \item The representations should also be relevant to the labels that are in the ontologies. For example, a model pre-trained on text will likely have very different embeddings than trained on an ontology, and may as such not be very useful.
  \item Some labels may be ambiguous, for example homonyms, which are concepts that have the same label but represent a different context.
 \end{itemize}

@@

 \subsubsection{Mice and men}
 The first data set considered consists of two anatomical ontologies. The first ontology describes the anatomy of mice and the second ontology the anatomy of men. Since they are similar creatures, there are many correspondences between the anatomy. The ontologies contain 1838 and 3298 nodes, and 1807 and 3761 edges, respectively. There are 1516 correspondences between the two ontologies.
 \paragraph{}
 The ontology is structured as a hierarchical tree with the only label being \emph{subClassOf}. This poses a few problems for some of the implementations as they take into account the edge labels. Since there are no edge labels, these implementations will not be different from their edge-less counterparts.
 \subsubsection{Medical}
 The second data set is larger, boasting 23692 and 16923 medical concepts with 31289 and 18932 relations. There are 18476 correspondences between the two ontologies.

@@

@@

  DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal word embedding model. This means it is possible to have a wide neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm. It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
  One adaptation over normal Deepwalk that was considered is switching between ontologies when on a concept from the correspondence set. For example, if both ontologies contain \textit{eye}, when the algorithm lands on the corresponding node, it will have a chance to switch to the other ontology. As such the sentence will contain concepts from both ontologies and they will move closer together. See \ref{sentences} for an example of the sentences generated by DeepWalk.

@@

@@

@@

  Possible reasons for the data causing bad results include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm. For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels. %TODO sowieso aanpassen maar ook aanpassen als ik 3e dataset heb.
  \paragraph{}
 The algorithm has been run on multiple data sets which are different. Despite that there is no significant difference in performance. For example, compare the F-measures for the medical dataset and the anatomy dataset. From Section \ref{results} we can see that both F-measures improve over the baselines, therefore the datasets used do not seem to influence the algorithm by much.
  \subsubsection{The system}
  Since the system parts are connected in sequence, if any of the steps in the software system contains an error, the whole system fails. This could cause all algorithms to learn badly or the results to be misinterpreted. The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers. If all of these systems work properly, the system is not the reason for the underperformance. I will analyse every part except for the context extractor, which will be analysed in the next section.

@@

  The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing ontology. The KD-tree has been tested by its creator and as such does not contain errors.
  \paragraph{Data loading}
  Since the preprocessing and context extraction works, we can conclude that the data is also loaded properly.
  \paragraph{Statistics and visualisation}
  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
  \paragraph{}
  Since every part works, the system is not faulty.

@@

  \subsubsection{Context extraction} \label{contextextraction}
  There are different context extractors for some of the different algorithms. I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model. If all three work well, the context extractors are not the cause of the underperformance.
  \paragraph{}
  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}. Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
  \paragraph{}
  For the Node2vec algorithms, the context extraction is more advanced. All edges are extracted from the ontology using Jena. Then, for every node the context is decided as every node it has an edge with. In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness. For the algorithms that also use the edge labels for context, double the context size is expected.
  \paragraph{}
  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up. For example "Adrenal vein" can be split up into "Adrenal" and "vein".
  The pre-trained model does not use any other form of context integration.
  \paragraph{}
  First, I obtained the number of edges from VOWLview\cite{vowlview}, an ontology graphing program, represented in Figure \ref{vowlfig}. This was necessary since the creators of the data did not share how many edges were in the database. With the actual number of edges, obtained, it is possible to compare them with the number of edges found. If these match, the context extraction works.

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{plots/vowlview}
  \caption[VOWLview of mice dataset]{The mice dataset visualized in VOWLview. It shows the hierarchical nature of the data, as subclasses circle their superclass. It also shows that many individual classes are not connected, and as such structure cannot be used in the matching process.}
  \label{vowlfig}
  \end{figure}

@@

 \subsubsection{Example: DeepWalk sentences} \label{sentences}
 Sentence lengths vary from 1 to about a hundred. The lower limit is due to the fact that some nodes do not have neighbours and as such the sentence is cut short. The upper limit not precise since the sentence end is random.

 Below are some examples of sentences.
 \begin{figure}[H]
 \paragraph{}
 \textcolor{Plum}{incus} \textcolor{red}{auditory\_bone} \textcolor{Plum}{\underline{incus}} \textcolor{blue}{ auditory\_ossicle ear\_part cymba\_conchae}
 \paragraph{}
  \textcolor{red}{brain\_nucleus brainstem\_nucleus red\_nucleus brainstem\_nucleus raphe\_pallidus\_nucleus brainstem\_nucleus trochlear\_iv\_nucleus brainstem\_nucleus nucleus\_of\_trapezoid\_body}
  \paragraph{}
  \textcolor{red}{hip\_joint hindlimb\_joint} \textcolor{Plum}{\underline{ankle\_joint}} \textcolor{blue}{joint\_by\_site cricoarytenoid\_joint}
  \label{jumpingsentence}
  \caption[Sentence that runs over both ontologies]{Example of a sentences that run over both ontologies. The words are color coded according to which ontology they occur in. Red is the mice ontology, blue the human ontology and purple words occur in both ontologies. Underlined words indicate a point at which the walker switches between the ontologies.}
 \end{figure}

 The first and third sentence both contain words that are in both ontologies. However, in the first sentence the switch does not occur immediately. The second sentence contains words from just one ontology. This will improve the embeddings for that ontology, but will not teach the algorithm about the mapping from one ontology to the other.

 \begin{figure}[H]
 \paragraph{}
 \textbf{thyroid\_gland\_left\_lobe}
 \label{singlesentence}
 \caption[Sentence with single word]{Some sentences contain only one word. Often these words refer to nodes with no neighbours.}
 \end{figure}
 \newpage
 \subsection{Evaluation}
 The goal of this study is to see if the developed ontology matching algorithm performs better than the best existing matchers. In this section I will define better.
 \subsubsection{Evaluation methods} \label{EvaluationMethods}
 Since for the used data the ground truth is available, comparison is straightforward. Namely, the algorithm that finds the most items that are also in the ground truth in the lowest number of attempts. This definition, however, has two parts: the number of correct attempts and the total number of attempts. This makes it hard to compare two algorithms, as one may be better with few attempts allowed whereas the other may be better with more attempts allowed.

@@

 %TODO F-pieken aanwijzen.
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/trained_ROC}
   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
   \label{ROC_trained}
  \end{figure}

@@

 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Generic_ROC}
   \caption[Precision-recall curve pre-trained mice]{Pretrained Word2vec algorithm.}
   \label{ROC_generic}
   \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering\includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{Random for comparison.}
   \label{ROC_untrained}
  \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Alternative_ROC}
   \caption[Precision-recall curve DeepWalk mice]{Alternative DeepWalk algorithm.}
   \label{ROC_alternative}
  \end{subfigure}
  \caption[Three more precision-recall curves]{Precision-recall trade-off curve for the results of three more algorithms.}
  \end{figure}
   \subsubsection{Medical data}
   TBD

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$]{The $F_1$-scores for the different matchers for the mice and medical datasets compared to the result of AML at OAEI 2015 \cite{oaei2015}}.
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Label Match & 0.6926 & 0.4905 \\
  Random & 0.6926 & 0.4905 \\
  Pre-trained & 0.6372 & 0.3874 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Multi-sense & 0.6926 & 0.4905 \\
  Deepwalk & 0.6926 & 0.4906 \\
  Alternative DeepWalk & 0.6372 & 0.4905 \\
  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\
  \end{tabular}
  \end{table}

  \subsection{Example }
  (cortical\_layer\_iii,external\_pyramidal\_cell\_layer)

 \newpage
 \subsection{Interpretation}

 \subsubsection{Unexpected results}
 \subsubsection{Expected results}

@@

 \subsection{Conclusions} \label{conclusions}
 %TODO conclusie: het werkt. Alleen niet beter dan de beste.
 The goal of this study was to answer the research question from Section \ref{researchquestion}:

@@

\paragraph{The algorithm uses distributed representations of concepts}
 From Section \ref{implementations} it is clear that every single algorithm uses distributed representations. To summarize:
\begin{description}
\item[pre-trained Word2vec] Uses existing distributed representations on every word in a label.
\item[Node2vec] All implementations of the Node2vec algorithms, monodirection, bidirectional and multi-sense, convert nodes into vectors.
\item[DeepWalk] Trains a normal distributed representation model on labels with the context generated from a random walk.
\end{description}
\paragraph{The algorithm finds relationships between concepts in ontologies}
This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
\paragraph{The algorithm performs well}
%TODO ook bij hypotheses weghalen
 One of the algorithms finds new relations. Therefore we can conclude that the algorithm can be used for ontology matching.

 All algorithms perform worse than the full AML ensemble. However, as detailed further in Section \ref{discussion}, there is potential for embedding methods.
\paragraph{}
 Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}.
 \paragraph{}
The results from all the different evaluation measures are in agreement. From those results we can conclude the following:

@@

 \subsection{Discussion} \label{discussion}
 %TODO gooi weg wat niet meer waar is
  %TODO Duidelijk maken waarom algoritme nog potentie heeft

@@
